\tool: Programmable, Efficient, and Scalable \\ Secure Two-Party Computation for Machine Learning

### 2018-05-06 ccs/conclude.tex
minor

>>>>

\section{Conclusion and Future Work}
\label{sec:conclude}

We presented \tool, the first
cryptographic-cost aware framework that generates efficient and
scalable \mpc protocols from high-level programs.
The generated protocols comprise combinations
of arithmetic and boolean circuits and have performance comparable to, or better than the previously known custom specialized
protocols from previous works.
The compiler is backed by formal semantics that help 
%it
%insert type coercions between boolean and arithmetic parts automatically while 
it maintain correctness, security,
and efficiency.

Currently, we are working on a front-end to translate Tensorflow code to \tool. The aim here is to provide a push button implementation to data scientists that generates secure implementations for their existing models.  
In the future, we would like to extend our security guarantees to malicious adversaries. However, we are currently unaware of a maliciously secure \mpc implementation for combinations of
arithmetic and boolean circuits. The cryptographic backends continue to improve and the modular design of \tool makes it easy to integrate with new backends. We will continue integrating with the best available backends.
Finally, we will explore the possibility of mechanically verifying the implementation of our compiler.

### 2018-05-06 ccs/ex.tex
minor

\subsection{Comparison with Yao-only approach}
Before we provide the formalization of our compiler, we show that for performance it it critical to use a mix of arithmetic and boolean circuits.
We demonstrate the performance benefits of mixed computation over boolean-only compute by comparing with previous tools CBMC-GC~\cite{cbmcgc} and ObliVM~\cite{oblivm} that are based on Yao's garbled circuits. As we already mentioned,  we are not the first to observe that Yao-only approach does not scale well beyond examples with small numbers of multiplications \cite{aby,tasty,autoS,secureml,minionn,chameleon}, especially for large-scale multiplications commonly found in Machine Learning (ML) algorithms -- the main use case of \tool.  
\dg{Speaking loosely,} multiplying two $64$-bit integers using arithmetic sharing requires only $2$ multiplications, whereas Yao requires at least $4096$ AES operations in the online phase.
Indeed, this is one of the main drivers behind development of various specialized MPC protocols in previous works \cite{secureml,minionn,shafindss} that we compare against in \sectionref{eval}.

The largest example benchmark in CBMC-GC is multiplication of two $8\times 8$ matrices for which it generates <FILL> gates and takes <FILL> seconds to run. In contrast, in \tool we use arithmetic sharing for this compute that generates <FILL> gates and completes in <FILL> seconds. We tried running CBMC-GC for multiplying two $20\times 20$ matrices and it timed out after 5 hours. In contrast, most of our benchmarks are much bigger. For example, we run the secure computation of a DNN for CIFAR-10 in 265 seconds which requires multiplying a $64\times576$ matrix with a $576\times1024$ matrix as a sub-computation. On the other hand, ObliVM scales to larger benchmarks with its use of Yao-pipelining \cite{yao-pipe}. We ran inner-product computations of varying lengths followed by a comparison in both ObliVM and \tool (see Table~\cite{oblivm-compare}). Our experiments show that we are atleast 30x faster than ObliVM due to our use of arithmetic sharing for inner-product computation.

\subsection{Cryptographic cost-aware compiler}
\label{sec:ccc}
One of the main challenges for our compiler is to split the compute between arithmetic and boolean parts well. 
As mentioned above, \tool is a cryptographic cost-aware compiler and uses the arithmetic and boolean costs of primitive operators and the inter-conversion costs to make the split. Cryptographic cost of converting an arithmetic share to a boolean share requires computing a garbled circuit for addition that is linear in size. Similarly, the cost of converting from boolean to arithmetic is computing a subtraction circuit inside garbled circuit that is again linear in size. ABY analyses all of these costs by running microbenchmarks for basic operations and interconversions (see Figures 2 and 3 in \cite{aby}). Based on these costs, our compiler has some hard constraints. For example, multiplication should always be performed in arithmetic circuit as the cost of boolean multiplication is much higher than  the cost of coercing from boolean to arithmetic, performing an arithmetic multiplication, and then coercing from arithmetic to boolean \dg{($\sim9x$ time $\&$ $\sim20x$ comm. in LAN setting)}. Since the performance gap between arithmetic and boolean is large, we believe that this choice is optimal for realistic network settings.
However, this is not the case for addition. In \tool, if both the operands of addition are boolean shared, we do the addition using boolean circuit, else we use arithmetic circuit. Hence, addition may be done in arithmetic or boolean depending on the operands. 
Finally, all the boolean operations such as comparison, shifts, multiplexors, etc are done using Yao.
We note that doing an optimal split between arithmetic and boolean is an \dg{NP-hard} problem and in this work, we use some heuristics based on costs observed using microbenchmarking. 
For the smaller benchmarks of our evaluation, we wrote ABY code directly and the circuits
generated by our compiler had about the same size as the  hand written code. 
%Moreover, for our machine learning benchmarks (such as linear classifier, DNNs, etc) these choices seem optimal.

>>>>

\subsection{Comparison with Yao-only approach}
Before we provide the formalization of our compiler, we show that for performance it it critical to use a mix of arithmetic and boolean circuits.
We demonstrate the performance benefits of mixed computation over boolean-only compute by comparing with previous tools CBMC-GC~\cite{cbmcgc} and ObliVM~\cite{oblivm} that are based on Yao's garbled circuits. As we already mentioned,  we are not the first to observe that Yao-only approach does not scale well beyond examples with small numbers of multiplications \cite{aby,tasty,autoS,secureml,minionn,chameleon}, especially for large-scale multiplications commonly found in Machine Learning (ML) algorithms -- the main use case of \tool.  
Roughly, multiplying two $64$-bit integers using arithmetic sharing requires only $2$ multiplications, whereas Yao requires at least $4096$ AES operations in the online phase.
Indeed, this is one of the main drivers behind development of various specialized MPC protocols in previous works \cite{secureml,minionn,shafindss} that we compare against in \sectionref{eval}.

The largest example benchmark in CBMC-GC is multiplication of two $8\times 8$ matrices for which it generates about a million gates and takes about ten seconds to run. In contrast, in \tool we use arithmetic sharing for this compute that generates <FILL> gates and completes in <FILL> seconds. We tried running CBMC-GC for multiplying two $20\times 20$ matrices and it timed out after 5 hours. In contrast, most of our benchmarks are much bigger. For example, we run the secure computation of a DNN for CIFAR-10 in 265 seconds which requires multiplying a $64\times576$ matrix with a $576\times1024$ matrix as a sub-computation. On the other hand, ObliVM scales to larger benchmarks with its use of Yao-pipelining \cite{yao-pipe}. We ran inner-product computations of varying lengths followed by a comparison in both ObliVM and \tool (see Table~\cite{oblivm-compare}). Our experiments show that we are atleast 30x faster than ObliVM due to our use of arithmetic sharing for inner-product computation.

\subsection{Cryptographic cost-aware compiler}
\label{sec:ccc}
One of the main challenges for our compiler is to split the compute between arithmetic and boolean parts well. 
As mentioned above, \tool is a cryptographic cost-aware compiler and uses the arithmetic and boolean costs of primitive operators and the inter-conversion costs to make the split. Cryptographic cost of converting an arithmetic share to a boolean share requires computing a garbled circuit for addition that is linear in size. Similarly, the cost of converting from boolean to arithmetic is computing a subtraction circuit inside garbled circuit that is again linear in size. ABY analyses all of these costs by running microbenchmarks for basic operations and interconversions (see Figures 2 and 3 in \cite{aby}). Based on these costs, our compiler has some hard constraints. For example, multiplication should always be performed in arithmetic circuit as the cost of boolean multiplication is much higher than  the cost of coercing from boolean to arithmetic, performing an arithmetic multiplication, and then coercing from arithmetic to boolean ($\sim9x$ more time $\&$ $\sim20x$ more communication in a LAN setting). Since the performance gap between arithmetic and boolean multiplication is quite large, we believe that this choice is optimal for realistic network settings.
However, this is not the case for addition. In \tool, if both the operands of addition are boolean shared, we do the addition using boolean circuit, else we use arithmetic circuit. Hence, addition may be done in arithmetic or boolean depending on the operands. 
Finally, all the boolean operations such as comparison, shifts, multiplexors, etc are done using Yao.
We note that doing an optimal split between arithmetic and boolean is an NP-hard problem and in this work, we use some heuristics based on costs observed using microbenchmarking. 
For the smaller benchmarks of our evaluation, we wrote ABY code directly and the circuits
generated by our compiler had about the same size as the  hand written code. 
%Moreover, for our machine learning benchmarks (such as linear classifier, DNNs, etc) these choices seem optimal.

### 2018-05-06 ccs/security.tex
minor

%\vspace{-0.2in}
\paragraph{Security theorem.} The protocols we generate provide
simulation-based security against a semi-honest adversary, in the
framework of ~\cite{gmw,can00,can01}. At a very high level, in this
framework, parties are modeled as non-uniform interactive turing
machines (ITMs), with inputs provided by an environment $\env$. An
adversary $\adv$, selects and ``corrupts'' one of the parties -
however, $\adv$ still follows the protocol specification. $\adv$
interacts with $\env$ that observes the view of the corrupted
party. At the end of the interaction, $\env$ outputs a single bit based on the output of the honest party and the view of the adversary. Two
different interactions are defined: the {\em real world} and an {\em
  ideal world}. In the real interaction, the parties run the protocol
$\prot$ in the presence of $\adv$ and $\env$. Let
$\real_{\prot,\adv,\env}$ denote the  distribution ensemble
describing $\env$'s output in this interaction. 
In the ideal interaction, parties send their inputs to  a
trusted functionality that performs the desired
computation truthfully. Let $\simu$ (the simulator) denote the
adversary in this ideal execution, and $\ideal_{\F,\simu,\env}$
the distribution ensemble describing $\env$'s output after
interacting with the ideal adversary $\simu$. A
protocol $\prot$ is said to {\em securely realize} a functionality
$\F$ if for every adversary $\adv$ in the real interaction, there is
an adversary $\simu$ in the ideal interaction, such that no
environment $\env$, on any input, can tell the real interaction apart
from the ideal interaction, except with negligible probability (in the
security parameter $\secparam$). More precisely, the above two
distribution ensembles  are computationally indistinguishable.

>>>>

%\vspace{-0.2in}
\paragraph{Security theorem.} The protocols we generate provide
simulation-based security against a semi-honest adversary, in the
framework of ~\cite{gmw,can00,can01} and provide provable security against all side-channel attacks.
At a very high level, in this
framework, parties are modeled as non-uniform interactive turing
machines (ITMs), with inputs provided by an environment $\env$. An
adversary $\adv$, selects and ``corrupts'' one of the parties -
however, $\adv$ still follows the protocol specification. $\adv$
interacts with $\env$ that observes the view of the corrupted
party. At the end of the interaction, $\env$ outputs a single bit based on the output of the honest party and the view of the adversary. Two
different interactions are defined: the {\em real world} and an {\em
  ideal world}. In the real interaction, the parties run the protocol
$\prot$ in the presence of $\adv$ and $\env$. Let
$\real_{\prot,\adv,\env}$ denote the  distribution ensemble
describing $\env$'s output in this interaction. 
In the ideal interaction, parties send their inputs to  a
trusted functionality that performs the desired
computation truthfully. Let $\simu$ (the simulator) denote the
adversary in this ideal execution, and $\ideal_{\F,\simu,\env}$
the distribution ensemble describing $\env$'s output after
interacting with the ideal adversary $\simu$. A
protocol $\prot$ is said to {\em securely realize} a functionality
$\F$ if for every adversary $\adv$ in the real interaction, there is
an adversary $\simu$ in the ideal interaction, such that no
environment $\env$, on any input, can tell the real interaction apart
from the ideal interaction, except with negligible probability (in the
security parameter $\secparam$). More precisely, the above two
distribution ensembles  are computationally indistinguishable.
